An Open Repository of Real-Time COVID-19 Indicators

### 2021-10-04 indicators/paper/paper.tex
Pass over Sect 2D

The revision tracking feature in the API assists in model-building and
evaluation. Figure~\ref{fig:dv_as_of} illustrates how one COVIDcast medical
claims signal evolved as it was revised across multiple issue dates, in four
different states, between June 1 and August 1, 2020. In each plot, the rightmost
ends of the lines correspond to estimates for the last day that data are
available for each issue date, which are generally the most tentative estimates,
and appear to be significantly biased upward in Arizona in June 2020, and
significantly biased downward in New York throughout June and July 2020.

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/dv_as_of.pdf}
  \caption{Estimated percentage of doctor's visits due to COVID-like illness
    displayed across multiple issue dates, with later issue dates adding
    additional data and revising past data from prior issue dates.}
  \label{fig:dv_as_of}
\end{figure}

@@

Figure~\ref{fig:backfill-compare} shows relative differences between early
indicator values, reported 10--90 days after the underlying events, and later 
versions at least four months later. As the distribution of these revision
amounts is highly skewed, the figure plots the 95th percentile of relative
change, showing that reported deaths can incur large relative error in initial
values, comparable to that in claims-based signals.  However, for deaths, as
well as cases, the revision pattern is not very systematic, with large
corrections typically occuring at a sparse subset of locations and times
(e.g., due to audits or backlogs being cleared, which can result in thousands of
cases or deaths can be  added or removed all at once).  This backfill is much
more difficult to predict than that of claims data, thus the latter (and other 
sources) may be useful for nowcasting cases and deaths while public health 
reports are being aggregated and corrected.

To reiterate a previous point, when training and validating forecast models that
use signals (on historical data), users will want to use data that was known
\textit{as of} the forecast date, not revised versions that only became
available much later. The COVIDcast API makes all historical versions available
and easily accessible for this purpose; and this feature plays a prominent role
in our own analysis of forecasting and hotspot prediction models appearing in a
companion paper \cite{McDonald:2021}.% Revisions to forecast targets, such as 
% cases and deaths, also complicate the evaluation of forecast models:
% comparisons of forecasts to the ground truth may shift when the ground truth
% is revised weeks later. Only by systematically tracking revisions can this
% effect be monitored.

>>>>

The revision tracking feature in the API assists in model-building and
evaluation. Figure~\ref{fig:dv_as_of} illustrates how DV-CLI, a medical claims
signal, evolved as it was revised across multiple issue dates, in four different
states, between June 1 and August 1, 2020. DV-CLI is similar to CHNG-CLI and
reflects outpatient visits with COVID-related symptoms (the two signals are
based on claims data provided by different data partners, which cover different
hospital systems). In each panel, the rightmost end of each colored line
corresponds to an estimate for the last day of available data for a given issue
date, which we can see tends to be significantly biased upward in Arizona in
June 2020, and significantly biased downward in New York throughout June and
July 2020.

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/dv_as_of.pdf}
  \caption{Estimated percentage of outpatient visits due to COVID-like illness 
    (DV-CLI) displayed across multiple issue dates, with later issue dates
    adding additional data and revising past data from prior issue dates.}
  \label{fig:dv_as_of}
\end{figure}

@@

Figure~\ref{fig:backfill-compare} shows relative differences between early
indicator values, reported 10--90 days after the underlying events, and later
versions at least four months later. As the distribution of these revision
amounts is highly skewed, the figure plots the 95th percentile of relative
change, showing that reported deaths can incur large relative error in initial
values, comparable to that in claims-based signals.  However, for deaths, as
well as cases, the revision pattern is not very systematic, with large
corrections typically occuring at a sparse subset of locations and times (e.g.,
due to audits or backlogs being cleared, which can result in thousands of cases
or deaths can be added or removed all at once).  This backfill is much more
difficult to predict than that of claims data, therefore the latter (and other
sources) may be useful for nowcasting cases and deaths while public health
reports are being aggregated and corrected.

To reiterate a previous point, when building forecast models (on historical
data) for retrospective evaluation purposes, users will want to use data that
was known \textit{as of} the forecast date, not revised versions that only
became available at a later time. Note that not only model training, but also
model assessment, can be affected by the revision process (comparisons of
forecasts to the ground truth may shift when the ground truth is revised weeks
later). Only by systematically tracking revisions can all these effects be
monitored and properly accounted for.  The COVIDcast API makes all historical
versions available and easily accessible for this purpose; and this feature
plays a prominent role in our own analysis of forecasting and hotspot prediction
models appearing in a companion paper \cite{McDonald:2021}.
